### 2013-01-31 mcmc.tex
are you converged?

...What figures should you make to check the chain?

@@

...How do you know you have run long enough?  Heuristically...

...Autocorrelation time

>>>>

...What do you do in high-dimensional spaces?  Note the issue
that---even in a unimodal posterior PDF---the most probable model
might not be at the set of parameter values that are reported if you
compute the parameter values to report in one-dimensional projections
of the posterior pdf.  This requires a figure to demonstrate.  What to
do here?

...What figures should you make to display the chain?

...If you are really good, you will pass forward a sampling.  How big
should it be?  Refer to Mackay here.

@@

A key question for an MCMC operator---\emph{the} key question in some
sense---is \emph{how long to run} to be sure of having reliable
results.
It is disappointing and annoying to many that there is no extremely
simple and reliable answer to this question.

The reason that there is no simple answer is that you can't really
ever know that you have sampled the full posterior pdf, and the reason
for \emph{that} is that if you \emph{could} know that, you would also
be able to solve the famously difficult discrete optimization
problem.\note{explain this remark and cite something here}
Another way to put it is that you might have two modes---two separated
regions of substantial total probability---in the posterior pdf that
are both important but separated by a large region of low probability.
If you are using a simple sampler, you could sample one of these modes
very well but the sampler will take effectively infinite time to find
the other mode.
Any test of convergence would be passed, but in fact the sampling
would be incomplete and not representative.
That is, knowing that you have a complete and representative sampling
is nearly impossible.

Heuristically, however, you have sampled long enough when you can see
that the (or each) walker has traversed the high-probability parts of
the parameter space many times in the length of the chain.
Or, equivalently, you have sampled long enough when the first half of
the chain shows very much the same posterior pdf morphology as the
second half of the chain, or indeed as any substantial subset.

...What plot should you make?  Make plots that demonstrate a non-converged and a converged chain.

...Autocorrelation time is the premier tool.  It is not a panacea, and why?
